Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-22 analysis/paper/paper.Rnw
added subsubsection header
fixed Makefile
updated Makefile for compiling paper.pdf

@@

For $n$ mice, $\Sigma$ is a $2n$ by $2n$ covariance matrix, while $V_g$ and $V_e$ are $2$ by $2$ covariance matrices. Estimates $\hat V_g$ and $\hat V_e$ are obtained via an expectation-maximization algorithm \citep{zhou2014efficient,gemma2}

@@

We generated scatter plots of pleiotropy test statistics vs. mediation LOD difference proportion values. Each
point represents a pairing of a local trait with a nonlocal trait. In all five scatter plots, we observe few
points in the upper right quadrant of the figure. That is, few pairs have high pleiotropy test statistics and
high mediation LOD difference values.

>>>>

\subsubsection{Two-dimensional, two-QTL scans}

@@

For $n$ mice, $\Sigma$ is a $2n$ by $2n$ covariance matrix, while $V_g$ and $V_e$ are $2$ by $2$ covariance matrices. Estimates $\hat V_g$ and $\hat V_e$ are obtained via an expectation-maximization algorithm \citep{zhou2014efficient,gemma2}.

@@

We generated scatter plots of pleiotropy test statistics vs. mediation LOD difference values.
Each point represents a pairing of a local trait with a nonlocal trait.
In all five scatter plots, we observe few
points in the upper right quadrant of the figure.
That is, few pairs have high pleiotropy test statistics and
high mediation LOD difference values.

<<>>=
include_graphics("../figures/Chr2_scatter.pdf")
@
